Binary companions of red giant stars in \apogee\ \DR: \\ Search method and catalog of $>$4,500 systems

### 2018-03-10 paper/1-catalog/twoface-catalog.tex
Captions and intro

% to-do list
% ----------
% - Make sure we don't use $K$ as a number of samples - that's $M$ - because $K$
%   is the velocity semi-amplitude!

@@

% define macros for text
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\sdssiv}{\project{\acronym{SDSS-IV}}}
\newcommand{\thejoker}{\project{The~Joker}}
\newcommand{\thecannon}{\project{The~Cannon}}
\newcommand{\DR}{\acronym{DR14}}
\newcommand{\RC}{\acronym{RC}}
\newcommand{\RGB}{\acronym{RGB}}
\newcommand{\quantile}[2]{\ensuremath{\textrm{Q}_{#1}}\left(#2\right)}

@@

Most of what is known about stellar companions comes from studies of
nearby main-sequence (MS) stars.
MS stars with companions have a large dynamic range of constituent and orbital
characteristics.
For example, binary stars have mass-ratios that span from $\approx 0.03$
to 1 (e.g., \citealt{Kraus:2008}), and have periods from days to
millions of years (e.g., \citealt{Raghavan:2010}).
\todo{multiplicity in general: occurrence rates}

Less is known about non-interacting or detached companions to evolved stars.
Such systems are interesting because they enable studying extreme outcomes or
conditions of star formation and multiplicity.
For example, evolved stars are typically much brighter than their MS
counterparts, which enables characterizing the stellar companion population
throughout the Galactic disk over a wide range of chemical abundances.
They also provide a means to study the outcomes of stellar engulfment or
common-envelope evolution: Do short-period companions exist around evolved
stars, and do their statistics constrain stellar evolution on the red giant
branch (RGB)?
\todo{motivate time-domain spectroscopy}

Time-domain radial-velocity measurements of stars contain information about
massive companions: even with two successive observations of a single star, a
difference in the measured radial velocities implies the existence of at least
one companion.
However, with few or imprecise radial-velocity measurements, the orbital
properties of the companion(s) are very poorly constrained (e.g.,
\citealt{Price-Whelan:2017}).
The vast majority of spectroscopic targets with repeat observations in the
largest (by number of objects) stellar spectroscopic surveys are often observed
just a few times with sparse, non-uniform phase coverage.
Most prior searches for companions using survey RV data have therefore
restricted their searches to only sources with many, high-precision epochs, so
that the orbital solution can be unambiguously determined (e.g.,
\citealt{Troup:2016}), or have used simple statistics computed from the data to
study multiplicity (e.g., $\textrm{RV}_\textrm{max}$; \citealt{Badenes:2017}).

@@

We use the primary data products from \apogee\ \DR\ (i.e. the \texttt{allStar}
and \texttt{allVisit} files) which contain 258,475 unique source IDs
(\texttt{APOGEE\_ID}) and 1,054,381 unique visits.
We select all stars with $\geq 3$ visits that each pass a set of quality cuts,
described below.
For each visit, we require that the visit velocity uncertainty is $< 100~\kms$
(\texttt{VRELERR}) and the following bits are not set in the \texttt{STARFLAGS}
bitmask: \texttt{PERSIST\_HIGH}, \texttt{PERSIST\_JUMP\_POS},
\texttt{PERSIST\_JUMP\_NEG}, \texttt{VERY\_BRIGHT\_NEIGHBOR}, \texttt{LOW\_SNR}.
For each star, we require that $0 < \log g < 4$ and the following bits are not
set in the \texttt{ASPCAPFLAGS} bitmask: \texttt{STAR\_BAD}.
After these cuts, and the requirement of $\geq 3$ visits for a given star, we
are left with \nvisits\ visits for \nstars\ unique sources.
\figurename~\ref{fig:nvisits} shows the number of stars in several bins of
number of visits that pass the above quality cuts: \todo{XX}\% of the stars in
\DR\ have $< 8$ visits.
\figurename~\ref{fig:loggteff} ...

@@

We perform our individual system fits---that is, make our posterior
samplings---under the following assumptions:
\begin{description}
\item[no multiplets] All radial-velocity variations of the primary star are
  induced by a single companion.
  This is motivated by the idea that triple star systems are usually
  hierarchical so that the period of the inner binary is typically much shorter
  than the orbital period of the outer body (\todo{CITATION NEEDED}).
  At present, we ignore the possibility of higher-order multiple systems.
  % \todo{revisit this - do we want to also sample over a long-term trend?}
\item[Kepler] Related to the first point, all velocity variations of the primary
  are gravitational, and we therefore ignore the possibility of coherent intrinsic variation from, e.g., stellar oscillations.
\item[SB1] All spectra are single-lined; that is, we assume that the secondary
  is significantly fainter and is thus undetected in the spectra.
  This assumption is motivated by the fact that we expect \RGB\ stars to be
  substantially more luminous than their typical companion.
  However, there are known main-sequence double-lined binary stars in the
  \apogee\ catalog (\citealt{El-Badry:2018}), and an expected but unknown
  fraction of \RGB--\RGB\ binaries.
\item[simple noise model] Measurements are unbiased and noise estimates are
  correct up to an unknown excess variance.
  All noise contributions result in Gaussian uncertainties on the individual
  radial-velocity measurements.
\end{description}

@@

We have visually inspected the inferred orbits for all systems in this sample
and have flagged systems with questionable or invalid fits.
The value of the flag is: 0, when the orbits look reasonable, 1, when the orbits
look reasonable but the value of the inferred excess variance is large, and 2,
when the orbits are clearly poor fits.
Many of the stars flagged as ``2'' look like they may be triple systems, as they
tend to have radial velocity variations over two distinct timescales that are
never well-fit by a single Keplerian orbit.
This flag is included in the catalog (\tablename~\ref{tbl:highK-unimodal}) as
the column \texttt{clean\_flag}; To select a clean sample of companions that
have been successfully vetted by-eye, select only stars with
\texttt{clean\_flag == 0}.

@@

We again visually inspect all systems in this sample and assign a flag based on
the apparent quality of the inferred orbits (see
\sectionname~\ref{sec:unimodal}).
Again, to select a clean sample of companions from this catalog that have been
successfully vetted by-eye, select only stars with \texttt{clean\_flag == 0}.

@@

Here we highlight a few interesting results from visualizing the properties of
companions in the unimodal and bimodal samples defined above (see \sectionname
s~\ref{sec:catalog-unimodal} and \ref{sec:catalog-bimodal}).
In all figures, we only plot companions with inferred orbits that pass our
visual inspection (\texttt{clean\_flag == 0}).
We additionally restrict to stars with $\log g > 2$ to avoid upper RGB stars
that may have coherent oscillations that mimic RV modulations from companions.

@@

In \figurename~\ref{fig:mass}, three interesting systems are immediately
obvious: two systems with bimodal period samplings in which both period modes
put the minimum companion mass below the Hydrogen-burning limit, and one system
in which $M_{2, \textrm{min}} > M_1$; We discuss these systems below

@@

\subsubsection{2M04582049+2232000 -- brown dwarf companion candidate}
% BD candidate

\todo{What to show?}

\subsubsection{2M20130687+2044173 -- brown dwarf companion candidate}
% BD candidate

\todo{What to show?}

\subsubsection{2M01231070+1801407 -- black hole companion candidate}
% NS/BH candidate

\todo{What to show?}

@@

\todo{Expectation from theory? What's special at 10 days?}

\todo{Mathieu et al. 2004}

\figurename~\ref{fig:PeK}, left panel, shows the normalized orbital period and
eccentricity for all systems in the high-$K$, unimodal sample, and, right panel,
the RV semi-amplitude.
We normalize the inferred periods by the orbital period of a companion at the
surface of the primary, $P_{\textrm{surface}}$:
To do this for all systems in this sample, we assume that all primary stars have
masses equal to the median mass over all stars with prior mass measurements in
this sample, $M_1 = 1.36~\msun$, and assume a companion mass also equal to the
median over minimum companion masses $M_{2, \textrm{min}} = 0.5~\msun$.
We then use the surface gravity, $\log g$, of the primary, and eccentricity to
compute
\begin{align}
    P_{\textrm{surface}} &= \frac{2\pi \, G^{1/4}}{(1-e)^{-3/2}} \,
        \left(\frac{M_1 + M_2}{M_1^{3/4}}\right) \,
        10^{-3/4\,\log g} \\
    &= XX ...
\end{align}
where we use $M_{2, \textrm{min}}$ as $M_2$.
There is a clear signature of circularization just under $P/P_{\textrm{surface}}
\approx 10$.
\todo{why is this novel with a large sample of giant stars}

% Notebook: Results
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{P-e-K}
\end{center}
\caption{%
TODO:
\label{fig:PeK}
}
\end{figure}

% Notebook: Results
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.7\textwidth]{ecc-dist}
\end{center}
\caption{%
TODO:
\label{fig:ecc}
}
\end{figure}

@@

% Notebook: "Residuals-vs-metadata"
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.7\textwidth]{residuals}
\end{center}
\caption{%
Histogram shows the distribution of normalized visit residuals (see
\eqname~\ref{eq:normresid}) for all \nvisits\ used in the final run of
\thejoker\ (i.e. with updated excess variance distribution parameters inferred
in \sectionname~\ref{sec:inferjitter}).
The orange curve shows that expected for Gaussian uncertainties.
The distribution appears mostly Gaussian over a large range of residual values,
with slightly more populated tails and evidence of a few catastrophic outliers.
\label{fig:residuals}
}
\end{figure}

\subsection{Impossible companions: coherent oscillations?}

\todo{The companions that don't make sense / can't be}

\todo{Semi-periodic variables, etc.}

@@

The other recent catalog searched for stellar and substellar companions to all
stars in \apogee\ \acronym{DR12} (including the RGB) that passed a series of
quality cuts, and had $\geq 8$ visits (\citealt{Troup:2016}).
For each star in the sample, orbits were fit to the visit RVs using a multi-step
orbit-fitting procedure: it starts by identifying significant periods and a few
harmonics of those periods, then fits a Keplerian orbit at each of these
harmonics using least-squares fitting (\citealt{De-Lee:2013}) with a modified
$\chi^2$ statistic that penalizes fits in which the phase coverage of the data
is poor.
This procedure is not guaranteed to provide a unique orbit solution.

Of the 382 companions released as a part of this previous search, only 188 of
the host stars passed the stellar parameter and quality cuts used to define the
parent sample in this work (see \sectionname~\ref{sec:data}).
We have looked at all of the overlapping stars to compare the previously derived
companion orbital properties to the posterior samplings derived with \thejoker.
We find that the comparisons fall in three categories:
(1) the parameters reported in \citet{Troup:2016} agree with the posterior
samplings, and the period distribution appears unimodal,
(2) the parameters reported in \citet{Troup:2016} identify one possible mode of
a likely multi-modal posterior pdf over orbital parameters, and
(3) the data changed significantly between \apogee\ \acronym{DR12} and \DR, so
no meaningful comparisons can be made; Roughly 1/3 of the comparison sample
falls into each class.
\figurename~\ref{fig:troup-unimodal} shows a few representative cases in which
the \citet{Troup:2016} orbital parameters (orbit shown as orange line in left
panels, parameters shown as orange + in right panels) is consistent with the
orbit samples from \thejoker.
\figurename~\ref{fig:troup-multimodal} shows a few representative cases in which
we find that the posterior pdf over orbital parameters is multimodal, and the
\citet{Troup:2016} orbit identifies one of these modes.
For completeness, \figurename~\ref{fig:troup-datachanged} shows two instances in
which the orbital parameters from \citet{Troup:2016} no longer make sense,
likely because the data changed between data releases.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{troup-unimodal.pdf}
\end{center}
\caption{%
TODO:
\label{fig:troup-unimodal}
}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{troup-multimodal.pdf}
\end{center}
\caption{%
TODO:
\label{fig:troup-multimodal}
}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{troup-data-changed.pdf}
\end{center}
\caption{%
TODO:
\label{fig:troup-datachanged}
}
\end{figure}

@@

Comment on things we could do with these samples hierarchical inference...

@@

\software{
    \package{Astropy} (\citealt{Astropy-Collaboration:2013}),
    \package{emcee} (\citealt{Foreman-Mackey:2013}),
    \package{IPython} (\citealt{Perez:2007}),
    \package{matplotlib} (\citealt{Hunter:2007}),
    \package{numpy} (\citealt{Van-der-Walt:2011}),
    \package{scikit-learn} (\citealt{Pedregosa:2011}),
    \package{scipy} (\url{https://www.scipy.org/}),
    \package{schwimmbad} (\todo{JOSS paper}),
    \package{sqlalchemy} (\url{https://www.sqlalchemy.org/}),
    \package{thejoker} (\todo{thejoker zenodo?}),
    \package{twobody} (\todo{twobody zenodo?}).
}

@@

>>>>

% to-do list
% ----------
% - Make sure we don't use $K$ as a number of samples - that's $M$ - because $K$
%   is the velocity semi-amplitude!
% - Figure out what to say about upper RGB stars / coherent oscillations!

@@

% define macros for text
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\sdssiv}{\project{\acronym{SDSS-IV}}}
\newcommand{\thejoker}{\project{The~Joker}}
\newcommand{\thecannon}{\project{The~Cannon}}
\newcommand{\DR}{\acronym{DR14}}
\newcommand{\DRtw}{\acronym{DR12}}
\newcommand{\RC}{\acronym{RC}}
\newcommand{\RGB}{\acronym{RGB}}
\newcommand{\quantile}[2]{\ensuremath{\textrm{Q}_{#1}}\left(#2\right)}

@@

Most of what is known about stellar companions comes from studies of
nearby main-sequence (MS) stars.
\todo{occurrence rates}
MS stars with companions have a large dynamic range of constituent and orbital
characteristics.
For example, binary stars have mass-ratios that span from $\approx 0.03$
to 1 (e.g., \citealt{Kraus:2008}), and have periods from days to
millions of years (e.g., \citealt{Raghavan:2010}).
Less is known about population properties of non-interacting or detached
companions to evolved stars.

Large spectroscopic surveys with repeat observations offer a novel way to study
binary star and companion populations.
Time-domain radial-velocity measurements of stars contain information about
massive companions: Even with two successive observations of a single star, a
difference in the measured radial velocities implies the existence of at least
one companion.
However, with few or imprecise radial-velocity measurements, the orbital
properties of the companion(s) are very poorly constrained (e.g.,
\citealt{Price-Whelan:2017}).
The vast majority of spectroscopic targets with repeat observations in the
largest (by number of objects) stellar spectroscopic surveys are often observed
just a few times with sparse, non-uniform phase coverage.
Most prior searches for companions using survey RV data have therefore
restricted their searches to only sources with many, high-precision epochs, so
that the orbital solution can be unambiguously determined (e.g.,
\citealt{Troup:2016}), or have used simple statistics computed from the data to
study multiplicity (e.g., $\textrm{RV}_\textrm{max}$; \citealt{Badenes:2017}).

@@

We use the primary data products from \apogee\ \DR\ (i.e. the \texttt{allStar}
and \texttt{allVisit} files) which contain 258,475 unique source IDs
(\texttt{APOGEE\_ID}) and 1,054,381 unique visits.
We select all stars with $\geq 3$ visits that each pass a set of quality cuts,
described below.
For each visit, we require that the visit velocity uncertainty is $< 100~\kms$
(\texttt{VRELERR}) and the following bits are not set in the \texttt{STARFLAGS}
bitmask: \texttt{PERSIST\_HIGH}, \texttt{PERSIST\_JUMP\_POS},
\texttt{PERSIST\_JUMP\_NEG}, \texttt{VERY\_BRIGHT\_NEIGHBOR}, \texttt{LOW\_SNR}.
For each star, we require that $0 < \log g < 4$ and the following bits are not
set in the \texttt{ASPCAPFLAGS} bitmask: \texttt{STAR\_BAD}.
After these cuts, and the requirement of $\geq 3$ visits for a given star, we
are left with \nvisits\ visits for \nstars\ unique sources.
\figurename~\ref{fig:nvisits} shows the number of stars in several bins of
number of visits that pass the above quality cuts: \todo{92}\% of the stars in
our parent sample have $< 8$ visits.
\figurename~\ref{fig:loggteff} shows the stellar parameters of all \nstars\
stars in the parent sample used in this work.

@@

We perform our individual system fits---that is, make our posterior
samplings---under the following assumptions:
\begin{description}
\item[no multiplets] All radial-velocity variations of the primary star are
  induced by a single companion.
  This is motivated by the idea that triple star systems are usually
  hierarchical so that the period of the inner binary is typically much shorter
  than the orbital period of the outer body (e.g., \citealt{Tokovinin:2018}).
  At present, we ignore the possibility of higher-order multiple systems.
  % \todo{revisit this - do we want to also sample over a long-term trend?}
\item[Kepler] Related to the first point, all velocity variations of the primary
  are gravitational, and we therefore ignore the possibility of coherent intrinsic variation from, e.g., stellar oscillations.
\item[SB1] All spectra are single-lined; that is, we assume that the secondary
  is significantly fainter and is thus undetected in the spectra.
  This assumption is motivated by the fact that we expect \RGB\ stars to be
  substantially more luminous than their typical companion.
  However, there are known main-sequence double-lined binary stars in the
  \apogee\ catalog (\citealt{El-Badry:2018}), and an expected but unknown
  fraction of \RGB--\RGB\ binaries.
\item[simple noise model] Measurements are unbiased and noise estimates are
  correct up to an unknown excess variance.
  All noise contributions result in Gaussian uncertainties on the individual
  radial-velocity measurements.
\end{description}

@@

We have visually inspected the inferred orbits for all systems in this sample
and have flagged systems with questionable or invalid fits.
The value of the flag is: 0, when the orbits look reasonable, 1, when the orbits
look reasonable but the value of the inferred excess variance is large, and 2,
when the orbits are clearly poor fits.
Many of the stars flagged as ``2'' look like they may be triple systems, as they
tend to have radial velocity variations over two distinct timescales that are
never well-fit by a single Keplerian orbit.
The stars flagged as ``1'' tend to be either upper RGB stars, where
astrophysical surface jitter can lead to RV modulations, or SB2 systems, where
absorption lines from the secondary confuse the RV pipeline and lead to strange
RV signals.
This flag is included in the catalog (\tablename~\ref{tbl:highK-unimodal}) as
the column \texttt{clean\_flag}; To select a clean sample of companions that
have been successfully vetted by-eye, select only stars with
\texttt{clean\_flag == 0}.

@@

We again visually inspect all systems in this sample and assign a flag based on
the apparent quality of the inferred orbits (see
\sectionname~\ref{sec:catalog-unimodal}).
Again, to select a clean sample of companions from this catalog that have been
successfully vetted by-eye, select only stars with \texttt{clean\_flag == 0}.

@@

Here we highlight a few interesting results from visualizing the properties of
companions in the unimodal and bimodal samples defined above (see \sectionname
s~\ref{sec:catalog-unimodal} and \ref{sec:catalog-multimodal}).
In all figures, we only plot companions with inferred orbits that pass our
visual inspection (\texttt{clean\_flag == 0}).
We additionally restrict to stars with $\log g > 2$ to avoid upper RGB stars
that may have coherent oscillations that mimic RV modulations from companions.

@@

In \figurename~\ref{fig:mass}, three interesting systems are immediately
obvious: two systems with bimodal period samplings in which both period modes
put the minimum companion mass below the Hydrogen-burning limit (brown dwarf
candidates), and one system in which $M_{2, \textrm{min}} > M_1$ (a neutron star
or black hole candidate).
These systems are being followed-up and will be studied in future work.

@@

@@

From studies of binary star systems in open clusters, it is clear that
short-period binaries tend to be more circular (have smaller eccentricities) as
compared to longer-period binaries of the same age (e.g.,
\citealt{Mathieu:2005}).
Within a given population of binaries, this manifests as an apparently steep
transition from a distribution of eccentricities to mainly circularized orbits
at some characteristic period that depends on the age and evolutionary state of
the population (see, e.g., \figurename~5 in \citealt{Mathieu:2005})---i.e. above
this critical value of the period (or log-period), systems have some
distribution of eccentricities, and below the eccentricities are close to zero.
Many studies have measured this ``circularization period,'' predominantly for
main-sequence binaries (e.g., \citealt{Meibom:2006, Kjurkchieva:2017}), and
have found that it tends to be between 5--20 days, depending on age (e.g.,
\citealt{Mathieu:1988}).
For giant stars, the circularization period appears to be longer, closer to
$\approx 100$ days (\citealt{Mayor:1984}).

Theories for the tidal circularization process generally rely on tidal
dissipation via eddy viscosity in the convective regions of stars to explain
this (e.g., \citealt{Zahn:1989}).
The circularization timescale and period should therefore depend on the size of
the convective region, and the stellar parameters of the primary star.
RGB stars are therefore excellent test-cases for these theories, since
they are fully-convective:
By comparing to (small) samples of giant star binaries in open clusters, it
seems that the circularization timescales predicted by eddy viscosity
dissipation at least qualitatively scale to giant stars
(\citealt{Verbunt:1995}).

It is less clear what to expect for red clump (\RC) stars:
RC stars are horizontal branch stars and have therefore already climbed the RGB.
Short period, circularized companions in place before or while on the RGB could
be engulfed, or will at least have been common-envelope with the evolving star.
However, it is difficult to select samples of \RC\ stars to study this process
because first-ascent RGB stars will have similar colors and stellar parameters.
\citet{Verbunt:1995} argue that companion orbits may be a way to separate the
two overlapping populations: eccentric, short-period orbits around stars near
the red-clump should be first-ascent giants.

The samples produced in this work provide excellent datasets to study tidal
circularization of companions to giant stars across a range of ages and
metallicities
However, our samples consist of a mix of subgiants, giants, and RC stars which
have distinct distributions in mass and stellar radius.
To visualize the distribution of systems in period--eccentricity space, we have
therefore computed normalized periods, where we normalize by the orbital period
of a typical companion on a circular orbit at the surface of the primary,
$P_{\textrm{surface}}$.
To do this for all systems in this sample, we assume that all primary stars have
masses equal to the median mass over all stars with prior mass measurements in
this sample, $M_1 = 1.36~\msun$, and assume a companion mass also equal to the
median over minimum companion masses $M_{2, \textrm{min}} = 0.5~\msun$.
We then use the surface gravity, $\log g$, of the primary, and eccentricity to
compute
\begin{align}
    P_{\textrm{surface}} &= \frac{2\pi \, G^{1/4}}{(1-e)^{-3/2}} \,
        \left(\frac{M_1 + M_2}{M_1^{3/4}}\right) \,
        10^{-3/4\,\log g}
\end{align}
where we use $M_{2, \textrm{min}}$ as $M_2$.

\figurename~\ref{fig:PeK}, left panel, shows this normalized orbital period and
eccentricity for all systems in the high-$K$, unimodal sample, and, right panel,
the RV semi-amplitude.
There is a clear signature of circularization just under $P/P_{\textrm{surface}}
\approx 10$.
\todo{what else can or should we say?}

% Notebook: Results
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{P-e-K}
\end{center}
\caption{%
\textit{Left panel:} Orbital period and eccentricity for all high-$K$ unimodal
systems with $\log g > 2$, with period values normalized by the orbital period
of a hypothetical companion at the surface of each primary star,
$P_{\textrm{surface}}$, assuming $M_1 = 1.36~\msun$ and $M_2 =0.5~\msun$.
Stars in the \apogee\ \DR\ red clump catalog are outlined in red.
The sharp transition from eccentric systems to almost all circular orbits at
$P/P_\textrm{surface} \approx 7$ is likely an outcome of tidal circularization.
\textit{Right panel:} Normalized period and inferred radial velocity amplitude
for the same systems.
Points below $P/P_\textrm{surface} = 1$ are likely systems where the primary and
companion mass assumptions used to compute $P_\textrm{surface}$ are invalid.
\label{fig:PeK}
}
\end{figure}

% Notebook: Results
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=0.7\textwidth]{ecc-dist}
% \end{center}
% \caption{%
% TODO:
% \label{fig:ecc}
% }
% \end{figure}

@@

% Notebook: "Residuals-vs-metadata"
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.6\textwidth]{residuals}
\end{center}
\caption{%
Histogram shows the distribution of normalized visit residuals (see
\eqname~\ref{eq:normresid}) for all \nvisits\ used in the final run of
\thejoker\ (i.e. with updated excess variance distribution parameters inferred
in \sectionname~\ref{sec:inferjitter}).
The orange curve shows that expected for Gaussian uncertainties.
The distribution appears mostly Gaussian over a large range of residual values,
with slightly more populated tails and evidence of a few catastrophic outliers.
\label{fig:residuals}
}
\end{figure}

@@

The other recent catalog searched for stellar and substellar companions to all
stars in \apogee\ \DRtw\ (including the RGB) that passed a series of quality
cuts, and had $\geq 8$ visits (\citealt{Troup:2016}).
For each star in the sample, orbits were fit to the visit RVs using a multi-step
orbit-fitting procedure: it starts by identifying significant periods and a few
harmonics of those periods, then fits a Keplerian orbit at each of these
harmonics using least-squares fitting (\citealt{De-Lee:2013}) with a modified
$\chi^2$ statistic that penalizes fits in which the phase coverage of the data
is poor.
This procedure is not guaranteed to provide a unique orbit solution.

Of the 382 companions released as a part of this previous search, only 188 of
the host stars passed the stellar parameter and quality cuts used to define the
parent sample in this work (see \sectionname~\ref{sec:data}).
We have looked at all of the overlapping stars to compare the previously derived
companion orbital properties to the posterior samplings derived with \thejoker.
We find that the comparisons fall in three categories:
(1) the parameters reported in \citet{Troup:2016} agree with the posterior
samplings, and the period distribution appears unimodal,
(2) the parameters reported in \citet{Troup:2016} identify one possible mode of
a likely multi-modal posterior pdf over orbital parameters, and
(3) the data changed significantly between \apogee\ \DRtw\ and \DR, so
no meaningful comparisons can be made; Roughly 1/3 of the comparison sample
falls into each class.
\figurename~\ref{fig:troup-unimodal} shows a few representative cases in which
the \citet{Troup:2016} orbital parameters (orbit shown as orange line in left
panels, parameters shown as orange + in right panels) is consistent with the
orbit samples from \thejoker.
\figurename~\ref{fig:troup-multimodal} shows a few representative cases in which
we find that the posterior pdf over orbital parameters is multimodal, and the
\citet{Troup:2016} orbit identifies one of these modes.
For completeness, \figurename~\ref{fig:troup-datachanged} shows two instances in
which the orbital parameters from \citet{Troup:2016} no longer make sense,
likely because the data changed between data releases.

@@

\todo{Comment on things we could do with these samples hierarchical
inference...}

@@

\software{
    \package{Astropy} (\citealt{Astropy-Collaboration:2013}),
    \package{emcee} (\citealt{Foreman-Mackey:2013}),
    \package{IPython} (\citealt{Perez:2007}),
    \package{matplotlib} (\citealt{Hunter:2007}),
    \package{numpy} (\citealt{Van-der-Walt:2011}),
    \package{scikit-learn} (\citealt{Pedregosa:2011}),
    \package{scipy} (\url{https://www.scipy.org/}),
    \package{schwimmbad} (\citealt{Price-Whelan:2017a}),
    \package{sqlalchemy} (\url{https://www.sqlalchemy.org/}),
    \package{thejoker} (\citealt{Price-Whelan:2017b}),
    \package{twobody} (\todo{twobody zenodo}).
}

@@

% Notebook: Compare Troup
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{troup-unimodal.pdf}
\end{center}
\caption{%
Four examples of stars that also appear in the \citet{Troup:2016} companion
catalog where our orbit samplings are unimodal, and agree well with the previous
orbit fits.
Left panels show the data from \apogee\ \DR\ (black markers), the orbit fit
(orange, thick line; \citealt{Troup:2016}), and 128 orbits computed from
posterior samples generated in this work (blue, thinner lines).
Right panels show the period and eccentricity of the orbit fit (orange, +
marker; \citealt{Troup:2016}) and the posterior samples from this work (blue
markers).
\label{fig:troup-unimodal}
}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{troup-multimodal.pdf}
\end{center}
\caption{%
Same as \figurename~\ref{fig:troup-unimodal}, but for four stars where we find a
multi-modal posterior sampling.
In this cases, the orbit fit from \citet{Troup:2016} generally identify one of
the possible period modes, but multiple orbit solutions are typically allowed.
\label{fig:troup-multimodal}
}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{troup-data-changed.pdf}
\end{center}
\caption{%
Same as \figurename~\ref{fig:troup-unimodal} and
\figurename~\ref{fig:troup-multimodal}, but for two stars in which no meaningful
comparison can be made because the visit velocities changed significantly
between \DRtw\ and \DR.
\label{fig:troup-datachanged}
}
\end{figure}
